---
title: "LTN Traffic Violations"
author: "@TheRealJimShady"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs/", output_file ="index.html") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Otto Street, SE17

```{r otto_street, echo=FALSE, fig.align="center"}

read_csv('otto_traffic_violations.csv', col_types = cols()) %>%
          pivot_longer(!date, names_to = "tickets", values_to = "count") %>% 
  filter(tickets != 'total') %>%
  filter(tickets != 'tickets_issued') %>%
  mutate(tickets = gsub('tickets_', '', tickets),
         date = as.Date(date, "%d/%m/%Y")) %>%
  ggplot(., aes(fill=tickets, y=count, x=date)) + 
    geom_bar(position="stack", stat="identity") +
  xlab("Month") +
  ylab('Tickets') +
  theme_classic() +
  theme(axis.text = element_text(size=12, colour = 'black'),
        axis.title = element_text(size=14, colour = 'black'))

```

Data: FOI request to Southwark Council, [available here](https://raw.githubusercontent.com/JimShady/ltn_traffic_violations/main/otto_traffic_violations.csv).

### Comments

-   It appears that for the first month of the scheme, all tickets were cancelled. In the data they were not strictly marked as this, but 100% were 'issued' with none of them open, paid or cancelled. I presume that they have been cancelled while residents get acustomed to the scheme.
-   Tickets were seemingly paused from 3rd December 2020 until 3 February 2021. Unsure of the reasons for this.
-   Despite clear signage and blocks in the road, since the beginning of February there are still 42 tickets per day being issued (compared to 90 in December 2020)

Pull requests to improve this page, or sending me similar data to compile for other LTNs is very welcome.

Like this and want more? I'd really appreciate a motivational coffee <https://ko-fi.com/therealjimshady>
